CMSAC_reveal_js

### 2025-10-10 CMSAC_reveal_js.qmd
intro slides

---
title: "CMSAC_reveal_js"
author: "Zach Culp, Josie Peterburs, Dr. Gregory J Matthews, Dr. Ryan P.A. McShane"
format: revealjs
editor: visual
---

@@

-   So, the final formula for the metric is: $$ \frac{wI_m(r,\hat{r})}{H(r) + H(\hat{r})} = \frac{\sum_r \sum_{\hat{r}} w(r,\hat{r}) * p(r, \hat{r}) \log{\frac{p(r,\hat{r})}{p(r)p(\hat{r})}}}{\log_2((n!)^2)}$$ \## Results

>>>>

---
title: "CMSAC_reveal_js"
author: "Zach Culp, Josie Peterburs, Dr. Gregory J. Matthews, Dr. Ryan P.A. McShane"
format: revealjs
editor: visual
---

@@

-   So, the final formula for the metric is: $$ \frac{wI_m(r,\hat{r})}{H(r) + H(\hat{r})} = \frac{\sum_r \sum_{\hat{r}} w(r,\hat{r}) * p(r, \hat{r}) \log{\frac{p(r,\hat{r})}{p(r)p(\hat{r})}}}{\log_2((n!)^2)}$$

## Results
